SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-02-16 scipy-1.0/paper.tex
ENH: intro: SciPy 1.0 -> convention belies "The SciPy 1.0 version numbering" doesn't fail to accurately represent the history of the project, but the version numbering convention does.

Recently, SciPy released version 1.0, a milestone that traditionally
signals a library's API (Applications Programming Interface) being
mature enough to be be trusted in production pipelines.  The SciPy 1.0
version numbering, however, belies the history of a project that has
become the standard which others follow and has seen extensive
adoption in research and industry.

>>>>

Recently, SciPy released version 1.0, a milestone that traditionally
signals a library's API (Applications Programming Interface) being
mature enough to be be trusted in production pipelines. This version 
numbering convention, however, belies the history of a project that has
become the standard which others follow and has seen extensive
adoption in research and industry.
